%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Ashwin Rajesh} \\ \vspace{1pt}
    \small +61 490718282 $|$ \href{mailto:ashwinr2k2@gmail.com}{\underline{ashwinr2k2@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/ashwin-rajesh-6a4960208/}{\underline{linkedin.com/in/ashwin}} $|$
    \href{https://github.com/VanillaViking}{\underline{github.com/VanillaViking}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Technology Sydney}{Ultimo, NSW}
      {Bachelor of Software Engineering (Honours) 79 WAM}{Feb 2021 -- Dec 2025 (expected)}
      \resumeItemListStart
        \resumeItem{Recipient of Best Capstone Poster Award 2025}
        \resumeItem{Dean's List 2024}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Full-Stack Software Developer}{Novermber 2022 -- July 2023}
      {Gecko.rent}{Ultimo, NSW}
      \resumeItemListStart
        \resumeItem{Implemented inventory tracking, product addons, review systems and more using MongoDB, GraphQL \& NextJS.}
        \resumeItem{Retained customers by decreasing load times by more than 90 seconds by using static paths and rendering.}
        \resumeItem{Developed a cronjob-based backend service to enable auto-scheduled emails. Brought in more product reviews.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Research Assistant}{Mar. 2024 -- Present}
      {University of Technology Sydney}{Ultimo, NSW}
      \resumeItemListStart
        \resumeItem{Built a research demo app (NextJS, Actix, MongoDB) with real-time charts, contour maps, and diagrams.}
        \resumeItem{Established a robust CI pipeline and reproducible builds using Nix, saved time during cloud migration.}
    \resumeItemListEnd

    \resumeSubheading
      {Casual Academic}{Feb 2025 -- Aug 2025}
      {University of Technology Sydney}{Ultimo, NSW}
      \resumeItemListStart
        \resumeItem{Mentored undergraduate students about fundamental embedded programming concepts.}
        \resumeItem{Assisted students on their practical embedded projects, giving them technical and design practice counsel.}
        \resumeItem{Evaluated students' performance and grade them based on their technical and practical proficiency.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Software Studio Project: Pantry Pilot} $|$ \emph{Cloudflare, Tanstack, OpenCV, YOLOv11}}{Jul 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Designed a Rust backend for running fresh produce image detection capable of high loads.}
            \resumeItem{Utilized multiple worker threads with multiple NN models. Implemented round-robin scheduling to assign requests}
            \resumeItem{Implemented object counting by combining OpenCV-style filters and algorithms with custom area processing.}
            \resumeItem{Reduced round-trip request time by 29\% compared to a single shared-model architecture.}
            \resumeItem{Created a camera component from scratch in React capable of uploading screenshots to the backend.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{PasteBuff} $|$ \emph{Rust, Tokio, Lua, Nix, Docker}}{Aug 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Architected and developed a self-hostable service to store and retrieve clipboards using Tokio asynchronous Rust.}
            \resumeItem{Developed a custom LRU cache with space-optimized storage of clipboard content.}
            \resumeItem{Currently integrating into Neovim as a plugin using Lua, along with from-scratch TCP socket handling.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Zyenyo Typing Test Bot} $|$ \emph{Java, Rust, NextJS, MongoDB, Docker}}{June 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Developed an application using Java to serve typing tests in Discord. Currently used in multiple large servers.}
            \resumeItem{Used MongoDB aggregation functions to perform statistical analysis on collected typing data.}
            \resumeItem{Helped create a performance rating algorithm, associating users' WPM, accuracy and prompt difficulty.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Open Source Contributions} $|$ \emph{Polybar, Gromit-MPX, React-Native-Dates, ClubVotingSystem, FuzzJudge, scrot}}{}
    \resumeSubHeadingListEnd

%-----------EXTRA CURR---------

\section{Extra Curricular}
    \resumeSubHeadingListStart
    \resumeSubheading
      {UTS Programming Society Executive}{October 2024 -- Present}
      {University of Technology Sydney}{Ultimo, NSW}
      \resumeItemListStart
        \resumeItem{Hosted Workshops such as Intro to programming, Vim Motions, Embedded Systems developement etc. }
        \resumeItem{Helped organise a programming competition. Designed and tested competition questions to challenge participants.}
        \resumeItem{Contributed to community projects such as the club voting system and competition judging system.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Rust, Typescript, C++, C, C\#, Java, Python, Bash} \\
     \textbf{Frameworks}{: NextJS, GraphQL, MongoDB, Postgres, Nginx, esp-idf, Arduino, AVR, SQLite} \\
     \textbf{Developer Tools}{: Git, Docker, Vim, Nix, Jira, Latex} \\
     \textbf{Libraries}{: tokio, serde, yolov11, onnx-runtime, opencv, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
